Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-22 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
fixing the bug of a hole in a hole
added section of growing based on buffering

\citetitle{Damen2008} \parencite{Damen2008}

@@

@@

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
where distance $d_G$ is the growing amount of each building. 
Parameter $d_\epsilon$ is the least distance allowed between two buildings.
We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
the corresponding two buildings will become too close during our growing step.
The two buildings are in the same group.

@@

\subsection{Simplifying merged buildings considering right angles}

We use an buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

\todo[inline]{more details in the below paragraph?}
We add two more constraints for a shortcut to be valid
when we use the Imai--Iri algorithm. 
The first one is that
a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
The second constraint is that a shortcut is not allowed to intersect the 
boundary of the original building.
If a shortcut does intersect, 
we will need to shrink the building instead of growing. Of course, we do not 
want to shrink.

\subsection{Growing}
If several buildings are close to each other at the start 
scale, we bridge them by line segments and take the merge of these 
buildings 
and bridges as one building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. Then we grow the  
building to the target shape. 
%
After finishing the growing, we take the goal scale as the 
start scale and repeat our continuous generalization.
\newline\indent
Our contribution is as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.

\subsection{Parameters for growing and simplifying}
The start scale is $1:S_\mathrm{s}$, and the goal scale is $1:S_\mathrm{g}$ 
($S_\mathrm{g}>S_\mathrm{s}$).
The area of a building should be larger than $a$ mm$^2$ on map.
A square at the start scale has area $a S_\mathrm{s}^2$ mm$^2$ at least.
A square at the goal scale has area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
mm.
Therefore, a square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm in order to survive.
In order to eliminate some small buildings, we define our growing distance as
\begin{equation}
\label{eq:d_G}
	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is our growing factor. A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.

\begin{figure}[tb]
	\centering
	\includegraphics{Growth}
	\caption{Growth.}
	\label{fig:Growth}
\end{figure}

The distance between two buildings should be larger than a threshold, say, 
$\epsilon$ mm on map \parencite{Stoter2009}.
In order to make the shape of a building simpler, we simplify buildings 
using the Douglas--Peucker algorithm \parencite{Douglas1973} with preservation 
of right angles.
To avoid using too many thresholds, we also use $\epsilon$ mm for the 
simplification algorithm, hence the real threshold distance 
is
\begin{equation}
\label{eq:d_epsilon}
d_\epsilon= \epsilon  S_\mathrm{g}.
\end{equation}

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on C\# (Microsoft Visual 
Studio 
2015) and ArcObjects SDK 10.4.1. 
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
We tested our method on a dataset from French Mapping Agency (IGN).
The dataset represents four towns (communes in French), i.e., Aussevielle, 
Denguin,  Poey-de-Lescar, and Siros, in the 
Pyr\'en\'ees-Atlantiques department, south-western France.
The scale of the dataset is $1:15{,}000$.
Our goal scale is $1:50{,}000$.

>>>>

@@

\subsection{Growing based on buffering}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a) for an example).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_G$, where $d_G$ is the growing distance, away 
from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha d_G \geq \sqrt{2}$. 
We set $\alpha d_G = 1.5$ so that a square joining is applied when an angle is 
smaller than $83.6 \degree$.

We use value $1.5$ so that we can keep

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_TwoKinds}
	\caption{Buffering a polygon using different kinds of joins.}
	\label{fig:Buffer_TwoKinds}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{Two typical ways of buffering a polygon.}
	\label{fig:Buffer_MiterLimits}
\end{figure}

If several buildings are close to each other at the start 
scale, we bridge them by line segments and take the merge of these 
buildings 
and bridges as one building.
For each building, either an original one or a merged one, at the start 
scale, 
we generate its target shape at 
the goal scale by enlarging and simplifying. Then we grow the  
building to the target shape. 
%
After finishing the growing, we take the goal scale as the 
start scale and repeat our continuous generalization.
\newline\indent
Our contribution is as follows. First, the buildings 
are enlarged continuously. At the same time, they are simplified. 
Second, we ensure that the distance between any pair of two buildings is 
always larger than a specified threshold.

@@

\textcite{Johnson2014}

@@

\subsection{Grouping buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
where distance $d_G$ is the growing amount of each building. 
Parameter $d_\epsilon$ is the least distance allowed between two buildings.
We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
the corresponding two buildings will become too close during our growing step.
The two buildings are identified as in the same group.

@@

\subsection{Simplifying merged buildings}

We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

\todo[inline]{more details in the below paragraph?}
We add two more constraints for a shortcut to be valid
when we use the Imai--Iri algorithm. 
The first one is that
a shortcut must be completely inside the grown building.
If a shortcut is outside,
we are not able to arrive at the shortcut by growing.
The second constraint is that a shortcut is not allowed to intersect the 
boundary of the original building.
If we allow this intersection, 
we need to shrink the building instead of growing. 
Of course, we do not want to shrink.

To avoid using too many thresholds, we also use $\epsilon$ mm for the 
simplification algorithm.

\subsection{Parameters for growing and simplifying}
Suppose that our start map is at scale $1:S_\mathrm{s}$, 
and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
The area of a building on map should be at least $a$ mm$^2$ so that the 
building is large enough to be perceived.
Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
mm$^2$ at least, and
a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
mm (see \fig\ref{fig:Growth}).
A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm so that it can survive when users zoom out from 
the start map to the goal map.
In order to eliminate small buildings, we define our growing distance as
\begin{equation}
\label{eq:d_G}
	d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is a growing factor. A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.

\begin{figure}[tb]
	\centering
	\includegraphics{Growth}
	\caption{Valid shortcut and invalid shortcut for Imai--Iri algorithm.}
	\label{fig:Growth}
\end{figure}

The distance between two buildings should be larger than a threshold, say, 
$\epsilon$ mm on map.
The real threshold distance is
\begin{equation}
\label{eq:d_epsilon}
d_\epsilon= \epsilon  S_\mathrm{g}.
\end{equation}

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on C\# (Microsoft Visual 
Studio 
2015) and ArcObjects SDK 10.4.1. 
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
We tested our method on a dataset from French Mapping Agency (IGN).
The dataset represents four towns (communes in French), i.e., Aussevielle, 
Denguin,  Poey-de-Lescar, and Siros, in the 
Pyr\'en\'ees-Atlantiques department, south-western France.
The scale of the dataset is $1:15{,}000$.
There are $2{,}590$ buildings (see \fig\ref{fig:Data}), 
which has $19{,}255$ edges in total.
Our goal scale is $1:50{,}000$.
